Manuscript

### 2021-08-16 Manuscript/Manuscript_Results.Rmd
clean: change package options namespace

# The following are already the default, but better be explicit
options(basren.probs = c(.05, .5, .95))
options(basren.sessions_folder = 'Sessions')

@@

As described in the methods, the selection of hyperparameters was achieved via the evaluation of sensibility and efficiency with a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.

>>>>

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = 'Sessions')

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.
